Combining living and fossil taxa into phylogenies: the missing data issue

### 2014-06-27 Manuscript/TEM_draft.tex
Updated tables results (8 missing Chains)

%10/06 - Missing 8 ML Chains
\begin{figure} 
\centering
\includegraphics[keepaspectratio=true]{Figures/TEM_Fig-results-BW.pdf}
\caption{Effect of missing data on Tree similarity.
$M_L$ is the percentage of living taxa with no morphological data,
$M_F$ is the percentage of missing data in the fossil record,
$M_C$ is the percentage of missing morphological characters.
The first row represent the Normalized Tree Similarity index using the Robinson-Foulds metric;
the second row represent the Normalized Tree Similarity index using the Triples metric.}
\label{Fig_Results}
\end{figure}

@@

\begin{table}
  \centering
  \linespread{1.0}
  \caption{$M_L$ non-parametric pairwise difference for Robinson-Fould metric in ML framework} %10/06 - Missing 8 ML Chains
  \input{Tables/ML_RF-ML_results}
  \label{ML_RF-ML_results}
\end{table}

\begin{table}
  \centering
  \linespread{1.0}
  \caption{$M_L$ non-parametric pairwise difference for Triples metric in ML framework} %10/06 - Missing 8 ML Chains
  \input{Tables/ML_Tr-ML_results}
  \label{ML_Tr-ML_results}
\end{table}

@@

\begin{table}
  \centering
  \linespread{1.0}
  \caption{$M_F$ non-parametric pairwise difference for Robinson-Foulds metric in ML framework} %10/06 - Missing 8 ML Chains
  \input{Tables/ML_RF-MF_results}
  \label{ML_RF-MF_results}
\end{table}

\begin{table}
  \centering
  \linespread{1.0}
  \caption{$M_F$ non-parametric pairwise difference for Triples metric in ML framework} %10/06 - Missing 8 ML Chains
  \input{Tables/ML_Tr-MF_results}
  \label{ML_Tr-MF_results}
\end{table}

@@

\begin{table}
  \centering
  \linespread{1.0}
  \caption{$M_C$ non-parametric pairwise difference for Robinson-Fould metric in ML framework} %10/06 - Missing 8 ML Chains
  \input{Tables/ML_RF-MC_results}
  \label{ML_RF-MC_results}
\end{table}

\begin{table}
  \centering
  \linespread{1.0}
  \caption{$M_C$ non-parametric pairwise difference for Triples metric in ML framework} %10/06 - Missing 8 ML Chains
  \input{Tables/ML_Tr-MC_results}
  \label{ML_Tr-MC_results}
\end{table}

>>>>

\begin{figure} 
\centering
\includegraphics[keepaspectratio=true]{Figures/TEM_Fig-results-BW.pdf}
\caption{Effect of missing data on Tree similarity.
$M_L$ is the percentage of living taxa with no morphological data,
$M_F$ is the percentage of missing data in the fossil record,
$M_C$ is the percentage of missing morphological characters.
The first row represent the Normalized Tree Similarity index using the Robinson-Foulds metric;
the second row represent the Normalized Tree Similarity index using the Triples metric.}
\label{Fig_Results}
\end{figure}

@@

\begin{table}
  \centering
  \linespread{1.0}
  \caption{$M_L$ non-parametric pairwise difference for Robinson-Fould metric in ML framework} 
  \input{Tables/ML_RF-ML_results}
  \label{ML_RF-ML_results}
\end{table}

\begin{table}
  \centering
  \linespread{1.0}
  \caption{$M_L$ non-parametric pairwise difference for Triples metric in ML framework} 
  \input{Tables/ML_Tr-ML_results}
  \label{ML_Tr-ML_results}
\end{table}

@@

\begin{table}
  \centering
  \linespread{1.0}
  \caption{$M_F$ non-parametric pairwise difference for Robinson-Foulds metric in ML framework} 
  \input{Tables/ML_RF-MF_results}
  \label{ML_RF-MF_results}
\end{table}

\begin{table}
  \centering
  \linespread{1.0}
  \caption{$M_F$ non-parametric pairwise difference for Triples metric in ML framework} 
  \input{Tables/ML_Tr-MF_results}
  \label{ML_Tr-MF_results}
\end{table}

@@

\begin{table}
  \centering
  \linespread{1.0}
  \caption{$M_C$ non-parametric pairwise difference for Robinson-Fould metric in ML framework} 
  \input{Tables/ML_RF-MC_results}
  \label{ML_RF-MC_results}
\end{table}

\begin{table}
  \centering
  \linespread{1.0}
  \caption{$M_C$ non-parametric pairwise difference for Triples metric in ML framework} 
  \input{Tables/ML_Tr-MC_results}
  \label{ML_Tr-MC_results}
\end{table}
